Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex
fibers preservation

\nt{state precisely some properties here, at least the 4 below}

@@

\item $\one$ seen as a $\Type_p$ is modal, ie $\modal \one =\one$.
\item (\cite{hottbook}, Lemma 7.7.2)
  Let $A:\Type$ and $B:A \to \Type_p^\modal$. Then $P\left(\prod_{a:A} (B\,
  a)\right)$. 
\item (\cite{hottbook}, Corollary 7.7.2) For any $A,B:\Type_p$,
  $\modal (A\times B) = (\modal A) \times (\modal B)$.
\item Let $A:\Type_p\modal$. Then for any $x,y:X$, $P(x=y)$.
\item (\cite{hottbook}, Theorem 7.7.4) 
  {\it (iv} can be extended to dependent product. Precisely~:

@@

Here, $\sum_{x:\modal X} (\modal f x = \eta_Y y)$ is modal, thus we
can define $$f:\modal \left(\sum_{x:X}  (f x = y)\right) \to
\sum_{x:\modal X} (\modal f x = \eta_Y y).$$
We need to check that the image of its fibers by $\modal$ are
contractible.
\kq{Finish that}
\end{proof}

@@

\begin{prop}\label{prop:sheaf-is-sheaf}
  $\Type_n^\modal$ is a sheaf.
\end{prop}

>>>>

@@

\item $\one$ seen as a $\Type_p$ is modal, ie $\modal \one =\one$.
\item (\cite{hottbook}, Lemma 7.7.2)
  Let $A:\Type$ and $B:A \to \Type_p^\modal$. Then $P\left(\prod_{a:A} (B\,
  a)\right)$. 
\item (\cite{hottbook}, Corollary 7.7.2) For any $A,B:\Type_p$,
  $\modal (A\times B) = (\modal A) \times (\modal B)$.
\item Let $A:\Type_p\modal$. Then for any $x,y:X$, $P(x=y)$.
\item (\cite{hottbook}, Theorem 7.7.4) 
  {\it (iv)} can be extended to dependent product. Precisely~:

@@

Here, $\sum_{x:\modal X} (\modal f x = \eta_Y y)$ is modal, thus we
can define $$\phi:\modal \left(\sum_{x:X}  (f x = y)\right) \to
\sum_{x:\modal X} (\modal f x = \eta_Y y).$$
We just need to check that the image of its fibers by $\modal$ are
contractible.

From definition of left exactness, one can deduce the following~:
\begin{lem}
  Let $A,B:\Type_p$. Let $f:A\to B$. If $\modal A$ and $\modal B$ are
  contractible, then so is $\fib f b$ for any $b:B$.
\end{lem}
We can rewrite $\fib \phi {x;p}$ in terms of the fiber of a fonction
$\fib {\eta_X} a \to \fib {\eta_Y} b$.

But we have the lemma~:
\begin{lem}
  Let $A:\Type_p$. Then for any $y:\modal A$, $\modal(\fib {\eta_A}
  y)$ is contractible.
\end{lem}

Finally, $\modal(\fib \phi {x;p})$ is contractible, and the result is proved.
\kq{Finish that}
\end{proof}

@@

\begin{prop}\label{prop:sheaf-is-sheaf}
  $\Type_n^\modal$ is a sheaf.
\end{prop}
\begin{proof}
  Firstly, we prove that $\Type_n^\modal$ is separated. Let $E:\Type$
  and $\chi:E \to \Type_n$, dense in $E$. Let $\phi_1,\phi_2:E \to
  \Type_n^\modal$, such that $\phi_1 \circ \pi_1 = \phi_2 \circ
  \pi_1$. Finally, let $x:E$. We show $\phi_1 x = \phi_2 x$ using
  univalence.

  As $\chi$ is dense, we have a term $m_x : \modal(\chi\, x)$.
  But as $\phi_2 x$ is modal, thus we can obtain a term $h_x : \chi\,
  x$. 
  As $\phi_1$ and $\phi_2$ are equal on $\sum_{e:E}\chi\, e$, we
  have an arrow $\phi_1 x \to \phi_2 x$.
  The same method leads to an arrow $\phi_2 x \to \phi_1 x$, and we
  prove they are each other inverse.

  Now, we prove that $\Type_n^\modal$ is a sheaf. Let $E:\Type$ and
  $\chi:E \to \HProp$, dense in $E$. Let $f:\sum_{e:E} \chi\, e \to
  \Type_n^\modal$. We want to extend $f$ to $E \to \Type_n^\modal$.

  We define $g$ as 
  $$g(e) = \modal \left( \fib \phi e \right), $$
  where
  $$\phi : \left(\sum_{b:\left(\sum_{e:E} (\chi\, e)\right)} (f\,
    b)\right) \to E$$
  defined by $\phi(x) = (x_1)_1$.
  Using the following properties on fibers, we can prove that it
  defines an equivalence.
  \begin{lem}
    Let $A,B,C:\Type_n$, $f:A\to B$ and $g:B\to C$.
    Then
    \begin{itemize}
    \item If $g$ is an embedding, then 
      $$\forall b:B,~\fib f b = \fib {g\circ f} {g\, b}.$$
    \item If all fibers of $f$ and $g$ are $n$-truncated, then
      $$\forall c:C,~\modal(\fib {g \circ f} c) =
      \modal \left(  
        \sum_{w:\fib g c} \modal (\fib f {w_1})
      \right).$$
    \end{itemize}
  \end{lem}

\end{proof}
